Co-citations in context

### 2019-05-28 cocit_r.tex
Updated conclusions paragraph in Introduction

Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around broad search terms. Within these disciplinary frameworks, we calculated expected journal pair frequencies using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations. We hypothesized that our approach would reduce model mis-specification and better simulate citation practice, in turn leading to different and more relevant conclusions. We found our model did, in fact, preserve the citation patterns found in the literature within an allowance for statistical sampling whereas the approach of Uzzi et al. does not. Those differences, due to sampling from within a discipline and more broadly, is manifest in journal pair z-scores whose signs change depending on the background dataset: the presence of such journal pairs has a conflicting effect on an article's characterization vis-\'a-vis novelty and conventionality depending on the background dataset. Our analysis of these semantically-themed citation networks challenges the universality of articles in the HCHN category having the highest probability of being hits as found in \cite{uzzi_atypical_2013}. For example, while HC remains highly correlated with hit articles in immunology and metabolism research, HN is not. In addition, while HN is highly correlated with hit articles in applied physics, HC is not.  Furthermore, we found that the categories demonstrating the highest percentage of hits is not robust with the parameters used to define hit articles and the threshold for highly novel citation patterns.

>>>>

Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around broad search terms. Within these disciplinary frameworks, we calculated expected journal pair frequencies using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations. We hypothesized that our approach would reduce model mis-specification and better simulate citation practice, in turn leading to different and more relevant conclusions. We found our model did, in fact, preserve the citation patterns found in the literature within an allowance for statistical sampling whereas the approach of Uzzi et al. does not. Those differences, due to sampling from within a discipline and more broadly, is manifest in journal pair z-scores whose signs change depending on the background dataset: the presence of such journal pairs has a conflicting effect on an article's characterization vis-\'a-vis novelty and conventionality depending on the background dataset. Our analysis of these semantically-themed citation networks challenges the universality of articles in the HCHN category having the highest probability of being hits as found in \cite{uzzi_atypical_2013}. For example, while HC remains highly correlated with hit articles in immunology and metabolism research, HN is not. In addition, while HN is highly correlated with hit articles in applied physics, HC is not.  Furthermore, we found that the categories demonstrating the highest percentage of hits is not robust with respect to varying parameters that define hit articles and the threshold for highly novel citation patterns.
